Evolution, functional diversity, regime shifts, hysteresis, and nonlinearity; ecosystem responses to environmental change.

### 2021-06-21 manuscript/article.Rmd
various

-   On the other hand, the opposite could occur: greater functional diversity could make a tipping point occur with less change in an environmental driver (i.e. may cause lower resilience) (Figure 2c in \@dakos2019b). This could occur if there is selection for greater tolerance that causes, incidentally, selection for lower growth rate, perhaps due to a tradeoff between the two traits.

@@

* Variation in amount of among strain variation, no variation in number of strains, no variation in strength or shape of the of the tradeoff.

@@

Each of the strains within each functional groups has its own parameter set and state variable. Thus a system with nine strains within each functional group has 27 state variables, plus another four (one for each of the four chemical substrates). Other than having potentially different parameter values (e.g. maximum growth rate and tolerance parameter) the dynamics of the strains in a functional were described by the same equations. Hence, when parameterised with multiple strains per functional group, but no variation among strains (within functional groups), the system behaves identically to when there is only one strain per functional group (see the `microxanox` R package *User Guide* for a demonstration).

@@

```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
#ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad1_old_strain_var.RDS"))
ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad_new2.RDS"))
ss_novar <- ss_sim_data[1,]
p1  <- plot_ss_result1(ss_novar$ss_res[[1]],
                ss_novar$CB_var_gmax_s,
                ss_novar$CB_var_h_s,
                ss_novar$SB_var_gmax_s,
                ss_novar$SB_var_h_s,
                ss_novar$PB_var_gmax_s,
                ss_novar$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

>>>>

-   On the other hand, the opposite could occur: greater functional diversity could make a tipping point occur with less change in an environmental driver (i.e. may cause lower resilience) (Figure 2c in @dakos2019b). This could occur if there is selection for greater tolerance that causes, incidentally, selection for lower growth rate, perhaps due to a tradeoff between the two traits.

@@

* Variation in amount of among strain variation, no variation in number of strains, no variation in strength or shape of the of any tradeoff.

@@

Each of the strains within each functional groups has its own parameter set and state variable. Thus a system with nine strains within each functional group has 27 state variables, plus another four (one for each of the four chemical substrates). Other than having potentially different parameter values (e.g. maximum growth rate and tolerance parameters) the dynamics of the strains in a functional were described by the same equations. Hence, when parameterised with multiple strains per functional group, but no variation among strains (within functional groups), the system behaves identically to when there is only one strain per functional group (see the `microxanox` R package *User Guide* for a demonstration).

@@

```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
#ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad1_old_strain_var.RDS"))
ss_sim_data <- readRDS(here("simulations/sim data/ss_res_CBvar.RDS"))
ss_novar <- ss_sim_data[1,]
p1  <- plot_ss_result1(ss_novar$ss_res[[1]],
                ss_novar$CB_var_gmax_s,
                ss_novar$CB_var_h_s,
                ss_novar$SB_var_gmax_s,
                ss_novar$SB_var_h_s,
                ss_novar$PB_var_gmax_s,
                ss_novar$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1
